\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-15 parts-infer-param.tex
add TODOs after the review
update
new 'Well-formed PH for K inference' property (to be completed)

@@

\begin{property}[Well-formed PH for parameter inference]\label{pro:wf-ph-K}
A PH is well-formed for parameter inference if and only if
it is well-formed for IG inference, and
the IG $(\Gamma, E)$ inferred by \pref{pps:inference-IG}
verifies the following property:
\begin{align*}
  \begin{split}
  \forall a \in \Gamma&, \forall b\in \GRNreg{a},
          \forall (i,j\in\levels{b}{a} \vee i,j\in\ulevels{b}{a}), \\
  & \quad \forall c \in \PHs, ( (b\neq a\wedge c=a) \vee (c\in\PHpredec{a}\setminus \Gamma \wedge b\in\PHdirectpredec{c})), \\
  & \qquad
                          \PHfrappe{b_i}{c_k}{c_l}\in\PHa \Leftrightarrow
                                  \PHfrappe{b_j}{c_k}{c_l}\in\PHa
  \end{split}
\end{align*}
\end{property}

>>>>

\todo{In this while section: add informal explanations and maybe more examples (see previous section).}

@@

\todo{makes it standalone: repeat the constraints for IG inference that are
actually necessary + check that we can do if if the IG is provided (then what
are the constraints on this IG)}

\begin{property}[Well-formed PH for parameter inference]\label{pro:wf-ph-K}
A PH is well-formed for parameter inference if and only if
it is well-formed for IG inference, and
the IG $(\Gamma, E)$ inferred by \pref{pps:inference-IG}
verifies the following property:
\todo{Define $c(\sigma)$ for $\sigma \in \textstyle\prod_{d \in \PHpredec{c}} \PHl_d$
(\ie the unique focal point)}
\begin{align*}
  \begin{split}
%   \forall a \in \Gamma&, \forall b\in \GRNreg{a},
%           \forall (i,j\in\levels{b}{a} \vee i,j\in\ulevels{b}{a}), \\
%   & \quad \forall c \in \PHs, ( (b\neq a\wedge c=a) \vee (c\in\PHpredec{a}\setminus \Gamma \wedge b\in\PHdirectpredec{c})), \\
%   & \qquad
%                           \PHfrappe{b_i}{c_k}{c_l}\in\PHa \Leftrightarrow
%                                   \PHfrappe{b_j}{c_k}{c_l}\in\PHa
      &
    \forall a \in \Gamma,
    \forall g \in X(a),
    \forall \sigma, \sigma' \in \textstyle\prod_{d \in g} \PHl_d,
    \forall b \in g,
    b \in \GRNreg{c},
    \forall c \in \PHdirectpredec{a} \setminus \Gamma,
      \\&\qquad
    b \in \reg{c},
    \forall (i,j \in \levels{b}{a} \vee i,j \in \ulevels{b}{a}),
%    \forall b_i \in \PHl_b,
    b_i \in \sigma,
%    b_i \in \levels{b}{a},
%    \forall b_j \in \levels{b}{a},
      \\&\qquad\qquad
    \sigma' = \sigma\{b_j\},
    %c_{\sigma} \in \PHl_c \wedge c_{\sigma'} \in \PHl_c,  %facultatif
    \PHfrappe{c(\sigma)}{a_i}{a_j} \in \PHa \Leftrightarrow
    \PHfrappe{c(\sigma')}{a_i}{a_j} \in \PHa
  \end{split}\\
  \begin{split}
    & \forall a \in \Gamma, \forall b \in \GRNreg{a},
      \forall (i,j \in \levels{b}{a} \vee i,j \in \ulevels{b}{a}), \\
    & \qquad \forall c \in \PHs, b \neq a,
      \PHfrappe{b_i}{a_k}{a_l} \in \PHa \Leftrightarrow
      \PHfrappe{b_j}{a_k}{a_l} \in \PHa
  \end{split}
\end{align*}
\end{property}
